\thesistitle

### 2019-07-28 sections/clonerefactor.tex
Getting somewhere

\begin{equation}\label{eq:variabilityclonerefactor}
\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(|E_1|+|E_2|)+(|E_3|+|E_4|)}*100
\end{equation}

@@

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
doA(a); //{1, -2, 3, -8, -9}
|\highlightYellow|doB();
doC(a);
|\highlightYellow|doD();
|\highlightYellow|doE();
|\highlightYellow|doF();
doG(a, b, c);
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doB(d, e, f);
|\highlightYellow|doA();
|\highlightYellow|doB();
|\highlightYellow|doC();
doB(d, e, f);
\end{javacode}}
\end{parcolumns}
\caption{Type 2R clones with equality arrays and variability percentages.}
\label{fig:trytoexpand}
\end{figure}

As an example, consider the clone fragment in figure \ref{fig:trytoexpand}.

>>>>

\begin{equation}\label{eq:variabilityclonerefactor}
\text{T2R Variability} = \frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(|E_1|+|E_2|)+(|E_3|+|E_4|)}*100
\end{equation}

@@

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|doA(); //{1, -2, -3, -4}
doB(a); //{5, -2, 7, -3, -4}
|\highlightYellow|doD(); //{8, -2, -3, -4}
|\highlightYellow|doE(); //{9, -2, -3, -4}
|\highlightYellow|doF(); //{10, -2, -3, -4}
doG(a, b); //{11, -2, 7, -3, -4}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|doA(); //{1, -2, -3, -4}
doC(a); //{6, -2, 7, -3, -4}
|\highlightYellow|doD(); //{8, -2, -3, -4}
|\highlightYellow|doE(); //{9, -2, -3, -4}
|\highlightYellow|doF(); //{10, -2, -3, -4}
doH(b); //{12, -2, 13, -3, -4}
\end{javacode}}
\end{parcolumns}
\caption{Type 2R clones with their equality arrays.}
\label{fig:trytoexpand}
\end{figure}

As an example, consider the clone fragment in figure \ref{fig:trytoexpand}. In this example, we have 2 clone classes. In the ``Try To Expand'' step, we will check whether we can create a clone class with larger clone instances on basis of the clones found in the previous step. We start with the largest clone class, measured in clone volume. We measure clone volume as the product of the amount of clone instances in a clone class and the amount of nodes in any of its instances.

In the example in figure \ref{fig:trytoexpand} the largest instance has a volume of:

\begin{equation}\label{eq:clonevolume}
3 \text{ nodes} * 2 \text{ clone instances} = 6
\end{equation}

Starting from this clone, we will try to expand it. We will include the previous node in the clone class and verify its variability threshold. In this case, using the formulas shown in section \ref{sec:t2rcheckglobalthres}, we can check whether this clone class would be valid by the variability threshold:

\begin{equation}\label{eq:variabilitycombined}
\frac{|\{(5,6)\}|}{(5+4+4+4)+(5+4+4+4)}*100 = \frac{1}{34}*100 = 15\%
\end{equation}
